GDPR: Is non-compliance profitable for Meta Platforms, Inc.?

### 2023-06-11 docs/research/LaTeX/research.tex
Fix references

\begin{figure}[H]
    \centering
    \includegraphics[width=1.00\textwidth]{violations-by-article}
    \caption{Number of violations by GDPR
    article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
    \label{fig:violations-by-article}
\end{figure}

@@

% Assess the impact of GDPR non-compliance on Meta Platforms' stock performance.
% Analyze stock price movements, market reactions to GDPR-related news, and
% changes in investor sentiment. Explore how GDPR issues have influenced
% investor confidence and the company's market capitalization.

@@

% Geography page 46 - advertising !!!

@@

\section*{Discussion}

% % Investigate the costs incurred by Meta Platforms in legal proceedings
% related to GDPR non-compliance. This includes expenses associated with hiring
% legal counsel, litigation, settlement agreements, and any ongoing legal
% obligations. Analyze the financial impact of these legal expenses on the
% company's profitability. Reputational Damage Assess the financial impact of
% reputational damage resulting from GDPR non-compliance. Investigate whether
% negative media coverage, public backlash, or loss of user trust have affected
% Meta Platforms' brand value or customer perception. Analyze any associated
% costs, such as brand recovery campaigns or decreased user acquisition rates.

% hard to assess

% https://www.law.com/corpcounsel/2021/11/24/as-regulators-hover-meta-expands-legal-department/

% https://www.law.com/corpcounsel/2022/11/10/meta-cuts-hit-legal-department-slamming-brakes-on-its-explosive-growth/?slreturn=20230510140111

% https://www.google.com/search?channel=fs&client=ubuntu&q=glasdoor+meta+lawyer+salary

\section*{Conclusion}

>>>>

% \begin{figure}[H]
%     \centering
%     \includegraphics[width=1.00\textwidth]{violations-by-article}
%     \caption{Number of violations by GDPR
%     article\cite{gdprFine1,gdprFine2,gdprFine3,gdprFine4,gdprFine5,gdprFine6,gdprFine7,gdprFine8,gdprFine9}}
%     \label{fig:violations-by-article}
% \end{figure}

@@

@@

@@

\section*{Discussion}
% Geography page 46 - advertising !!!

% state the results of each graph state what I want the readers to see from each
% graph

% connections

The limitations of this study are that it does not consider the legal expenses
incurred by \textit{Meta Platforms, Inc.} in relation to GDPR non-compliance.
This includes expenses associated with hiring legal counsel, litigation,
settlement agreements, and any ongoing legal obligations. It also does not
consider the financial impact of reputational damage resulting from GDPR
non-compliance. Moreover, it does not investigate whether negative media
coverage, public backlash, or loss of user trust have affected \textit{Meta
Platforms'} brand value or customer perception. Further research could be done
into those areas.
\section*{Conclusion}
